EpisoDAS - DAS-based password generation \\ using episodic memories

### 2018-01-20 paper/AVI2018/paper.tex
...

\usepackage{booktabs} % For formal tables

@@

% % DOI
% \acmDOI{10.475/123_4}
% 
% % ISBN
% \acmISBN{123-4567-24-567/08/06}
% 
% %Conference
% \acmConference[AVI2018]{ACM Woodstock conference}{July 2018}
%               {Rome, Italy}
% \acmYear{2018}
% \copyrightyear{2018}
% 
% 
% \acmArticle{4}
% \acmPrice{15.00}

@@

\author{Toshiyuki Masui}
% \authornote{Is this necessary?.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Keio University}
  \streetaddress{Endo}
  \city{Fujisawa}
  \state{Kanagawa}
  \postcode{43017-6221}
}
\email{masui@masui.org}

@@

@@

\begin{figure}
  % \includegraphics[width=8cm,bb=0 0 840 792]{figures/DAS.png}
  % \includegraphics[width=8cm,bb=0 0 320 321]{figures/DASexample.jpg}
  \includegraphics[width=12cm,bb=0 0 1000 667]{figures/AndroidLock.jpg}
  \caption{An example DAS pattern for Android.}
  \label{AndroidLock}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1332 1118]{figures/Easy.png}
  \caption{Easily creating problems}
  \label{Easy}
\end{figure}

@@

Remembering a special old episode is fairly hard for most people, but
remembering an attribute of an old friends seems to be much easier.

\section{Evaluation}

@@

速度

速度
拡張機能を利用すると
記憶しているパスワード入力よりも高速なぐらいで入力できる

覚えることが要らなくなった
公開しても大丈夫
  ググれる
* マスターパスワードが要らない

問題づくり

使い回しが駄目

サイトごとのカスタマイズが大変

覗き見は危険

ひとつのHTML

強度

@@

% \begin{acks}
% \end{acks}

% \bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

>>>>

% \usepackage{booktabs} % For formal tables

@@

% % DOI
% \acmDOI{10.475/123_4}
% 
% % ISBN
% \acmISBN{123-4567-24-567/08/06}
% 
%Conference
\acmConference[AVI2018]{International Conference on Advanced Visual Interfaces}{May 2018}
              {Resort Riva del Sole, Castiglione della Pescaia, Grosseto (Italy)}
\acmYear{2018}
\copyrightyear{2018}
% 
% 
% \acmArticle{4}
% \acmPrice{15.00}

@@

\author{Toshiyuki Masui}
% \authornote{Is this necessary?.}
% \orcid{1234-5678-9012}
\affiliation{%
  \institution{Keio University}
  \streetaddress{5322 Endo}
  \city{Fujisawa}
  \state{Kanagawa}
  \postcode{252-8520}
}
\email{masui@masui.org}

@@

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10002978.10002991.10002992.10011618</concept_id>
  <concept_desc>Security and privacy~Graphical / visual passwords</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}
\ccsdesc[500]{Security and privacy~Graphical / visual passwords}

\keywords{Passwords, Visual passwords, Authentication}

@@

\begin{figure}
  % \includegraphics[width=8cm,bb=0 0 840 792]{figures/DAS.png}
  % \includegraphics[width=8cm,bb=0 0 320 321]{figures/DASexample.jpg}
  \includegraphics[width=12cm,bb=0 0 1000 667]{figures/AndroidLock.jpg}
  \caption{Pattern lock for Android.}
  \label{AndroidLock}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1678 1728]{figures/Easy.png}
  \caption{Easily creating problems}
  \label{Easy}
\end{figure}

@@

Recalling a special old episode is fairly hard for most people, but
recalling an attribute of an old friends seems to be much easier.

@@

\subsection{Authentication speed}

Using EpisoDAS, very small amount of time is required for
the authentication process.
For a skilled computer user,
selecting answers based on the secret is a little bit slower than
typing a password on a computer with a hardware keyboard, but
EpisoDAS is faster on smartphones and tablet computers.

% 拡張機能を利用すると
% 記憶しているパスワード入力よりも高速なぐらいで入力できる

\subsection{Forgetting passwords}

The biggest advantage of using EpisoPass is that users don't have to
remember long password strings.

After the authors began using EpisoPass,
we have been having no problem forgetting passwords of any kind.

As long as a user have the seed string and question-answer data,
he can easily generate passwords by running
EpisoPass and answering the questions.

The seed string and question-answer data can be put on a public place
if they include enough amount of secrets.

If a question is based on old unforgettable episodic memory,
there is little chance of losing the password for a service
as long as the seed string and questions are available.

If the user's memory is related to an episode that took place 20 years
ago, say, and the user clearly still remembers the episode now, it is
unlikely the episode will be forgotten in the future.

\subsection{Universal}

EpisoDAS is implemented as a single HTML file that includes a JavaScript
script for password calculation.
We can put the HTML file on the Web or in a handy USB memory device
and access it from any Web browser.
If the questions are properly selected and nobody knows the correct answet to
the questions,
the data can be put on a public Web page or save it in a secure
repository like GitHub.
The data set of the authors are put on the Web, and it can be easily
found using Web search engines.
It means that the passwords used by the authors can be generated
even when the data is not kept locally.

\subsection{Security strength}

The strength of the generated passwords depends on the number and 
level of secrecy of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but measuring the strength of secret questions is an area where more study is needed.
% \marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is
% considerably more than a billion (closer to 10 thousand billion,
% (US) or 10 million million (UK).}
Using ten secret questions each with twenty answers, where each answer is considered equally likely,
an attacker would need to cover a search space of over ten trillion ($20^{10}$) values to check
every potential combination of answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
This represents roughly the same entropy as using a random 8-character Latin-alphabet
password, for which the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.

\subsection{Creating questions}

The quality of the questions is key to using EpisoDAS effectively.  If
the episode is shared by someone else, this other person might easily
be able to answer the question and generate the user's password.
%
The episode related to each question should therefore not be known to any other person,
and the episode should be unforgettable.
%
Finding such episodes seems difficult at first,
but using the method shown in the last section,
it is not super-difficult to recall
many trivial episodes which are unforgettable but
nonetheless not important to other people.

Questions such as ``Who did you like best?'' should be avoided,
since friends or family might know the user's tastes, thereby allowing 
others to select the correct answer.
Also, memories related to taste is more fragile than memories of facts.

% \subsection{Question reuse}
% 
% 使い回しが駄目
% どこかのサイトのパスワードが流出し、
% そのEpisoPassデータが公開されていたら
% ブルートフォースで答がわかってしまうから
% 問題を使い回すことは好ましくない

\subsection{Browser extension}

EpisoDAS browser extension is very useful, but creating the extension
is cumbersome because there is no standard login form for
different Web services.
%
The browser extension should first realize that the Web page is a login page
of a Web service (e.g. Amazon),
and then it should be able to get the ID of the user
and know where the result of EpisoDAS calculation should be pasted.

\subsection{Sholder surfing}

Simple DAS authentication is known to be fragile for ``shoulder surfing''
attacks\cite{Aviv:2017:TBS:3134600.3134609}.
If the secret pattern is simple enough and
the pattern can be easily observed over the user's shoulder,
attackers can easily 再現する the login pattern.

This problem is common to all the DAS-based authentication systems,
and great care should be taken when drawing a secret in the public.
EpisoDAS users can use complex DAS patterns
because there is no risk of forgetting the pattern,
because the user can use EpisoDAS even when he does not remember the
secret pattern.

\subsection{Forgetting pattern risks}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}
